---
title: "HW7 HW8a"
author: "Data Science 2"
editor: visual
format:
  html:
    embed-resources: true
execute:
  echo: true
  message: false
  warning: false
output: 
  code_folding: false
---

```{r setup}
library(tidyverse)
library(tidytext)
library(schrute)
library(topicmodels)
library(dplyr)
library(tidyr)
library(stringr)
library(ggplot2)
office <- theoffice

```

> Since `dplyr`, `tidyr`, `stringr`, and `ggplot2` are all part of `tidyverse`, they don't need to be loaded separately, so you could shorten this code chunk by removing those lines. You could also remove `office <- theoffice` and just refer to `theoffice` in the rest of your code, but what you have works fine too.

# The Office

Let's continue to work with *The Office* text from the [schrute](https://cran.r-project.org/web/packages/schrute/index.html) package.

# Primary Topics

For each season (not each episode anymore), determine the primary topics for the show using 1) a TF-IDF approach and 2) an LDA approach. You should do at least some cleaning of the data to exclude words that don't make sense.

# Cleaning

```{r, cleaning}
office_words <- office |>
  unnest_tokens(word, text) |>
  anti_join(stop_words |> distinct(word)) |>
  filter(str_detect(word, "^[a-z]+$")) |>
  select(index, season, word )

office_stop <- c("yeah", "hey", "uh", "um", "gonna", "guy",
                 "guys", "okay", "ok", "oh", "huh", "hmm", 
                 "ah", "alright","yep", "yea")

characters <- c("michael", "jim", "pam", "dwight", 
                "kevin", "angela", "oscar", "ryan", 
                "creed", "darryl", "karen", "jo", 
                "toby", "stanley","phyllis", 
                "andy", "kelly","meredith", "erin", 
                "jan", "holly")

# I used my memory from watching the show to remove 
# characters that appeared in either big roles or several seasons. 

office_words <- office |>
  unnest_tokens(word, text) |>
  filter(str_detect(word, "^[a-z]+$")) |>
  anti_join(stop_words, by = "word") |>
  filter(!word %in% office_stop) |>
  filter(!word %in% characters) 

```

> Instead of manually listing the character names, you could try using the `babynames` dataset, which would be more thorough in case there were any names that you missed. You could create the `characters` dataset by using an `inner_join` between `office_words` and `babynames`. Once again, what you have works, but just another option to consider.

# TF-IDF

```{r, tfidf}
top_season_words <- office_words |>
    count(season, word, name = "n") |>
  group_by(season) |>
  mutate(TF = n / sum(n)) |>
  ungroup() |>
    left_join(
    office_words |>
      distinct(season, word) |>
      count(word, name = "Dt") |>
      mutate(
        DF_adj = Dt / (1 + n_distinct(office_words$season)),
        IDF_adj = log(1 / DF_adj)), by = "word") |>
    mutate(TFIDF_adj = TF * IDF_adj) |>
  group_by(season) |>
  slice_max(TFIDF_adj, n = 10) |>
  arrange(season, desc(TFIDF_adj)) |>
  ungroup()


top_season_words |>
  mutate(word = reorder_within(word, TFIDF_adj, season)) |>
  ggplot(aes(TFIDF_adj, word, fill = factor(season))) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~season, scales = "free", ncol = 3) +
  scale_y_reordered() +
  labs(
    title = "Top TF-IDF Words by Season in The Office",
    x = "TF-IDF",
    y = "Word"
  ) +
  theme(axis.text.y = element_text(size = 5))
```

> If you want, you could collapse this code into a single pipeline instead of saving each step as its own dataframe. The code that you have above makes it easier to see what goes on in each step by breaking it down, but may be less efficient.

# LDA

```{r, lda}
office_dtm <- office_words |> 
  count(season, word) |> 
  filter(n >= 5) |> 
  cast_dtm(season, word, n)

office_lda <- LDA(office_dtm, k = 9)

office_topics <- tidy(office_lda, matrix = "beta")

top_terms_office <- office_topics |>
  group_by(topic) |>
  slice_max(beta, n = 10) |>
  ungroup()

top_terms_office |>
  mutate(term = reorder_within(term, beta, topic)) |>
  ggplot(aes(beta, term, fill = factor(topic))) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~topic, scales = "free") +
  scale_y_reordered() +
  labs(title = "Primary Topics in The Office (LDA)",
    x = "Beta (Word Probability)",
    y = "Term")
```

> Similarly to the section above, you could combine some of this code into a single pipeline. For example, you could replace the first few steps with:\
> `office_dtm <- office_words |> count(season, word) |> filter(n >= 5) |> cast_dtm(season, word, n)`

```{r, lda2}
season_topics <- tidy(office_lda, matrix = "gamma") |>
  rename(season = document)

ggplot(season_topics, aes(x = factor(season), 
                          y = gamma, fill = factor(topic))) +
  geom_col() +
  labs(title = "Topic Distribution Across Seasons",
    x = "Season",
    y = "Topic Probability",
    fill = "Topic")
```

> Your visualizations throughout the HW look great - very easy to read/understand and great use of color!
